Characterization and Photometric Performance of the Hyper Suprime-Cam Software Pipeline.

### 2017-04-28 draft/ms_v5.tex
cModel S/N

%% ------------------------------------------------------------------------------------ %%
%% Fig: Magnitude v.s S/N for galaxies
\begin{figure*}
    \begin{center}
        \includegraphics[width=\textwidth]{fig/synpipe_galaxy_sn}
    \end{center}
    \caption{
        Relation between input magnitudes (\textbf{left}: $i$-band; \textbf{right}:
        $g$-band) of synthetic galaxies $\log (\mathrm{S}/\mathrm{N})$ as measured 
        by \hscpipe{} \cmodel{} photometry. 
        Lines and contours are similar to Fig \ref{fig:star_sn}
        }
    \label{fig:cmodel_sn}
\end{figure*}
%% ------------------------------------------------------------------------------------ %%

@@

%% ------------------------------------------------------------------------------------ %%
%% Fig: Accuracies of the cModel color for galaxies
\begin{figure*}
    \begin{center}
        \includegraphics[width=\textwidth]{fig/synpipe_galaxy_color}
    \end{center}
    \caption{
        Accuracies of the color measurements for synthetic galaxies via the
        differences between input and \forced{} \cmodel{} colors.
        The \textbf{upper panels} and \textbf{lower panels} are for $g-i$ and $i-y$
        colors separately.
        The \textbf{left} column shows the relation between input magnitude (x-axis) and
        the color difference, and the \textbf{right} column uses the input colors as
        the x--axis.
        The lines and contours legend is identical to the plot in 
        Fig \ref{fig:psf_color}.
        }
    \label{fig:cmodel_color}
\end{figure*}
%% ------------------------------------------------------------------------------------ %%

@@

    Typical \tract{} in the Wide layer contains ${\sim}400000$ extended objects with 
    $i_{\mathrm{CModel}} < 25.5$ mag. 
        We randomly inject ${\sim}40,000$ synthetic galaxies into each \tract{}.

    so we inject additional ${\sim}10$\% extended 
    objects to the images. 
    Using an approach similar to that for synthetic stars, we select 
    galaxy samples for photometric comparisons. Synthetic galaxies that are located within 2 pixels 
    of the centroids of real objects are removed from the sample  (these represent ${\sim}3$--$7$\% of the input sample). After imposing quality cuts on the  recovered synthetic galaxy sample (see Appendix \ref{app:qc} for details), we have ${\sim}30,000$
    galaxies in each \tract{}.

    We find that \hscpipe{} mis-classifies less than $1$\% of these objects as point sources
    in the good-seeing \tract{}.
    But the fraction of misclassified galaxies increases to $4$\% in the
    bad-seeing \tract{}. We will discuss star/galaxy separation further in Section \ref{ssec:sg}.

    We define a sample of highly blended galaxies  by imposing the cut $b>0.05$.
    Due to the extended nature of galaxies, the $b$ distribution of synthetic 
    galaxies is more skewed toward high values (especially for the bad-seeing \tract{}) compared to the b distribution of stars.
    About $7$--$9$\% of synthetic galaxies are highly blended with $b>0.05$.
    The fraction is only slightly higher in the bad-seeing \tract{}, and the
    $g$-band has the highest fraction of highly blended galaxies \alexie{I don't understand here. Is this just a question of seeing? Is thid because the g-band has worse seeing. It seems in contradiction with the previous phrase.}. In our plots, we will highlight highly blended galaxies and we will discuss blending effects further in Section \ref{ssec:blendedness}.

@@

    Figure \ref{fig:cmodel_sn} shows the relation between the input
    magnitudes and the \s2n{} of synthetic galaxies.  The  \s2n{} is the ratio  of the \cmodel{} flux and its uncertainty.    The \s2n{} used here is the average one for extended object. \alexie{What do you mean here? You have a clound of points for each object, not a mean value of SN per mag bin. Needs to be calrified.}

 Figure  \ref{fig:cmodel_sn} shows  that the \cmodel{} photometry displays a well-behaved relation between input magnitude and output \s2n{}.  Compared to stars, the \s2n{} from \cmodel{} for synthetic galaxies shows a larger
    scatter at fixed input magnitude. This is likely due to the fact that galaxies have a wider range in sizes and shapes than point sources.  In $i$ band, a typical $25.2$ mag galaxy has \s2n{}${\sim}20$ from \cmodel{}, but 
    there are also galaxies at the same magnitude which have \s2n{} below 5. The HSC Wide layer can detect galaxies as faint as $i{\sim}26.0$ mag but the 
    sample becomes incomplete at these faint magnitudes.
    It also introduces a selection bias if galaxies with certain structural properties  (e.g., more extended and lower surface brightness)
    are harder to detect than others.
    HSC survey data users who want to select flux-limited galaxy samples,
    or who intend to study the population of faint (e.g., high-$z$) galaxies should
    keep this in mind.  Finally, we also find that  a worse seeing leads to a lower \s2n{} at fixed magnitude 
    (see Fig \ref{fig:psf_s2n} for $i$-band).

>>>>

%% ------------------------------------------------------------------------------------ %%
%% Fig: Magnitude v.s S/N for galaxies
\begin{figure*}
    \begin{center}
        \includegraphics[width=\textwidth]{fig/synpipe_galaxy_sn}
    \end{center}
    \caption{
        Relation between input magnitudes (\textbf{left}: $i$-band; \textbf{right}:
        $g$-band) of synthetic galaxies $\log (\mathrm{S}/\mathrm{N})$ as measured 
        by \hscpipe{} \cmodel{} photometry. 
        Lines and contours are similar to Fig \ref{fig:star_sn}.
        The truncation in $i$ band input magnitude is caused by the magnitude limit 
        of COSMOS galaxies used in this test. 
        }
    \label{fig:cmodel_sn}
\end{figure*}
%% ------------------------------------------------------------------------------------ %%

@@

%% ------------------------------------------------------------------------------------ %%
%% Fig: Accuracies of the cModel color for galaxies
\begin{figure*}
    \begin{center}
        \includegraphics[width=15cm]{fig/synpipe_galaxy_color}
    \end{center}
    \caption{
        Accuracies of the color measurements for synthetic galaxies via the
        differences between input and \forced{} \cmodel{} colors.
        The \textbf{upper panels} and \textbf{lower panels} are for $g-i$ and $i-y$
        colors separately.
        The \textbf{left} column shows the relation between input magnitude (x--axis) and
        the color difference, and the \textbf{right} column uses the input colors as
        the x--axis.
        The lines and contours legend is identical to the plot in 
        Fig \ref{fig:psf_color}.
        }
    \label{fig:cmodel_color}
\end{figure*}
%% ------------------------------------------------------------------------------------ %%

@@

    Typical \tract{} in the Wide layer contains ${\sim}400000$ extended objects with 
    $i_{\mathrm{CModel}} < 25.5$ mag. 
    We randomly inject ${\sim}40,000$ synthetic galaxies (additional ${\sim}10$\%) 
    into each \tract{}, and will not create over-crowded situation.
    Using similar approach for synthetic stars, we select galaxy samples for 
    photometric comparisons. 
    Synthetic galaxies that are located within 2 pixels of the centroids of real 
    objects are removed from the sample (they represent ${\sim}3$--$7$\% of the 
    input sample). 
    After imposing quality cuts on the recovered synthetic galaxy sample 
    (see Appendix \ref{app:qc} for details), we have ${\sim}30,000$ galaxies in 
    each \tract{}.

    We find that \hscpipe{} mis-classifies lower than $1$\% of these objects as 
    point sources in the good-seeing \tract{}.
    But the fraction of misclassified galaxies increases to $4$\% in the
    bad-seeing \tract{}. 
    We will discuss star/galaxy separation further in Section \ref{ssec:sg}.

    We define a sample of highly blended galaxies by imposing the cut 
    $b>0.05$\footnote{We already removed the ambiguously blended objects. 
    These objects have high blendedness, but are still distinctive.}.
    Due to the extended nature of galaxies, the $b$ distribution of synthetic 
    galaxies is more skewed toward high values (especially for the \texttt{badSeeing}
    \tract{}) compared to the b distribution of stars.
    About $7$--$9$\% of synthetic galaxies are highly blended with $b>0.05$.
    The fraction is slightly higher in the \texttt{badSeeing} \tract{}, and 
    therefore the $g$ band also has higher fraction of highly blended galaxies.
    In our plots, we will highlight highly blended galaxies and will discuss 
    blending effects further in Section \ref{ssec:blendedness}.

@@

    Figure \ref{fig:cmodel_sn} shows the relation between the input magnitudes and the 
    \s2n{} of synthetic galaxies.  
    The \s2n{} is the ratio  of the \cmodel{} flux and the flux error measured by 
    \hscpipe{}.
    Here the adopted \s2n{} corresponds to the average \s2n{} over entire footprint. 
    The center of the galaxy typically has high \s2n{} than this value.

    Figure \ref{fig:cmodel_sn} shows that the \cmodel{} photometry displays a 
    well-behaved relation between input magnitude and output \s2n{}.  
    Compared to stars, the \s2n{} from \cmodel{} for synthetic galaxies shows a larger
    scatter at fixed input magnitude. 
    This is likely due to the fact that galaxies have a wider range in sizes and shapes 
    than point sources.  
    In $i$ band, a typical $25.2$ mag galaxy has \s2n{}${\sim}20$ from \cmodel{}, but 
    there are also galaxies at the same magnitude which have \s2n{} below 5. 
    The HSC Wide layer can detect galaxies as faint as $i{\sim}26.0$ mag but the 
    sample becomes incomplete at these faint magnitudes.
    This also introduces a selection bias if galaxies with certain structural 
    properties (e.g., more extended and lower surface brightness) are harder to detect
    than others.
    HSC survey data users who want to select flux-limited galaxy samples,
    or who intend to study the population of faint (e.g., high-$z$) galaxies should
    keep this in mind.  
    Finally, we also find that a worse seeing leads to a lower \s2n{} at fixed 
    magnitude (see Fig \ref{fig:psf_s2n} for $i$-band).
